---
title: "About"
author: "zael8"
date: "21 listopada 2015"
output: html_document
---

The purpose of this application is to estimate the probability of the malignant breast cancer. The  Mammographic Mass Data Set  is used in order to estimate a logistic regression model that calculates the probabilities with respect to several variables. The dataset can find here:
https://archive.ics.uci.edu/ml/datasets/Mammographic+Mass


The list of libraries being used:


```{r, message=F, warning=F}
library(dplyr)
library(zoo)
library(shiny)
library(rpart)


```

The data loading. The missing values are replaced by the median value of the particular variable. 

```{r}
data1<- read.csv("mammographic.dat", header = FALSE, sep= "," , skip = 10, na.strings = "?")
colnames(data1)<- c("BIRADS", "Age", "Shape", "Margin", "Density", "Severity")
data1$BIRADS<-as.numeric(data1$BIRADS)
data1$Age<-as.numeric(data1$Age)
data1$Shape<- as.numeric(data1$Shape)
data1$Margin<- as.numeric(data1$Margin)
data1$Density <-  as.numeric(data1$Density)
data1<- na.aggregate(data1, FUN= median)
```


Please find below the estimated model’s summary:

```{r}
model <- glm(Severity~BIRADS+Age+Shape+Margin+Density, data = data1, family = "binomial")
summary(model)
```


Attribute Information:

6 Attributes in total (1 goal field, 1 non-predictive, 4 predictive attributes) 

1. BI-RADS assessment: 1 to 5 (ordinal, non-predictive!) 
2. Age: patient's age in years (integer) 
3. Shape: mass shape: round=1 oval=2 lobular=3 irregular=4 (nominal) 
4. Margin: mass margin: circumscribed=1 microlobulated=2 obscured=3 ill-defined=4 spiculated=5 (nominal) 
5. Density: mass density high=1 iso=2 low=3 fat-containing=4 (ordinal) 
6. Severity: benign=0 or malignant=1 (binominal, goal field) 


